\documentclass[10pt]{article}

\usepackage[left=0.6in,top=0.6in,right=0.6in,bottom=0.6in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{parskip}

\pagenumbering{gobble}
\setlist[itemize]{noitemsep, topsep=0pt}

% Section formatting
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]

\begin{document}

%-------------------- HEADER --------------------%

\begin{center}
    {\LARGE \textbf{DEON GEORGE}} \\
    +91 7558908998 | Kottayam, Kerala \\
    \href{https://www.linkedin.com/in/deon-george-vadakkel/}{LinkedIn} |
    \href{https://github.com/deon-george}{GitHub} |
    \href{https://app.mulearn.org/profile/deongeorge-1@mulearn}{MuLearn} |
    \href{https://www.behance.net/deongeorgeArt}{Behance}
\end{center}

%-------------------- OBJECTIVE --------------------%

\section*{OBJECTIVE}

Motivated B.Tech student passionate about Coding, AI/ML, and UI/UX Design. Proficient in Python, C, HTML, CSS, Canva, and Figma. Interested in Agentic AI and building impactful technology solutions.

%-------------------- EDUCATION --------------------%

\section*{EDUCATION}

\textbf{B.Tech in Computer Science and Engineering} \hfill 2023 -- 2027 \\
St. Joseph's College of Engineering and Technology (KTU), Palai, Kerala

\textbf{Class 12} \hfill 2018 -- 2020 \\
St. Antony's Public School, Anakkal

\textbf{Class 10} \hfill 2017 -- 2018 \\
St. Antony's Public School, Anakkal

%-------------------- SKILLS --------------------%

\section*{SKILLS}

\textbf{Programming:} Python, C, HTML, CSS \\
\textbf{Tools:} Git, GitHub, VS Code, Figma, Canva, Adobe Express \\
\textbf{Operating Systems:} Windows, MacOS, Linux (2+ years experience) \\
\textbf{Concepts:} AI/ML Basics, Agentic AI, Prompt Engineering


%-------------------- EXPERIENCE --------------------%

\section*{EXPERIENCE}

\textbf{Design Team Member, SAEI SJCET Palai} \hfill Jan 2025 -- Jan 2026
\begin{itemize}
    \item Designed posters using Figma, Canva, and Adobe Express.
    \item Collaborated with team members to create visually engaging content.
\end{itemize}

\textbf{MuLearn Learner} \hfill Sep 2023 -- Present
\begin{itemize}
    \item Secured 3rd place in ScratchX (A Game Development Competition).
    \item Achieved 2nd place in Think Ovation Ideathon.
    \item Completed  30 days musprint challenge.
    \item Reached Level 4.
\end{itemize}

\textbf{AI-Integrated Digital Marketing Intern, IPSR Solutions Ltd} \hfill Feb 2025 -- Mar 2025
\begin{itemize}
    \item Worked on AI-based marketing strategies and campaign optimization.
\end{itemize}

\textbf{National Cadet Corps (NCC)} \hfill 2020 -- 2023
\begin{itemize}
    \item Actively served as an NCC cadet, demonstrating discipline, leadership, and teamwork.
    \item Assisted in organizing and hosting various events, war demos, and competitions including Best Cadet selection, RDC competition, and obstacle running events.
    \item Successfully completed and passed both the B Certificate and C Certificate examinations during the three-year tenure.
\end{itemize}

\textbf{Volunteer – Byte Arena, Asthra 10.0 Tech Fest} \hfill 2025
\begin{itemize}
    \item Volunteered for Byte Arena, a mystery-solving competition conducted during Asthra 10.0.
    \item Assisted in coordinating a multi-round event involving debugging-based clue solving, crossword challenges, and logical problem-solving tasks.
    \item Acted as a “culprit” in the final interrogation round, contributing to an interactive and immersive experience for participants.
\end{itemize}



%-------------------- PROJECTS --------------------%

\section*{PROJECTS}

\textbf{Customer Relationship Management System (C \& SQLite)} \\
Developed a menu-driven Customer Relationship Management System using C language with SQLite as the database backend. The system manages customer records, stores data efficiently, and performs operations such as adding, updating, deleting, and retrieving customer information. \\
\href{https://github.com/deon-george/micro-project_CRMS}{GitHub Link}


\textbf{CLI-Based Travel Itinerary Generator (Multi-Agent System)} \\
Developed a command-line travel itinerary generator using a multi-agent system as the final project of the MuLearn Agentic AI Bootcamp. The system coordinates multiple agents to gather inputs, process travel preferences, and generate structured travel plans efficiently. \\
\href{https://github.com/deon-george/multi_agent_travel_cli}{GitHub Link}


\textbf{Pocket Diary – Chrome Extension} \\
Developed a minimalist Chrome extension to instantly capture, store, and export ideas efficiently. Designed for quick note-taking with a simple and distraction-free interface. \\
\href{https://github.com/deon-george/Pocket_diary}{GitHub Link}

\textbf{Retro Space Shooter – Asthra 9.0 Tech Fest Project} \\
Developed a 2D space shooter game featuring a spaceship navigating through asteroids and alien enemies. Implemented hand gesture controls to steer and shoot using computer vision techniques. Players start with three lives and score points by dodging obstacles and eliminating enemies. \\
\textbf{Tech Stack:} Pygame, OpenCV, MediaPipe \\
\href{https://github.com/deon-george/Retro_Space_shooter}{GitHub Link}



%-------------------- ACHIEVEMENTS --------------------%

\section*{ACHIEVEMENTS}

\begin{itemize}
    \item \textbf{1st Place} – SAEINDIA Bio-Mimicry college level (2025)
    \item \textbf{2nd Place} – Mobile App Development Competition, SAEINDIA college level (2025)
    \item \textbf{Best Position} - IEEE-CS/RAS Web Competition for College of Engineering Karunagappally (Aug 2025)
\end{itemize}

%-------------------- LANGUAGES --------------------%

\section*{LANGUAGES}

English, Malayalam

\end{document}

